---
title: "coding_exercise"
author: "Colleen Hoskins"
date: "2024-10-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("setup.R")
```

```{r}
data("knz_bison")
```

Create a new column in the bison dataset that calculates the individual’s age at the time of observation.

animal age = rec_year - animal_yob

```{r}
knz_bison %>%
   mutate(animal_age = rec_year - animal_yob)
```


Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
filter(knz_bison, animal_weight <= 100)
```

Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
knz_bison %>%
  ggplot(aes(y = animal_weight, x = animal_sex)) +   
  geom_boxplot()
```

```{r}
knz_bison %>%
  levene_test(animal_weight ~ animal_sex)
```

```{r}
knz_bison %>% 
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE) 
```

